Supplementary Material \\

### 2022-01-20 supplementary.tex
Updates from Overleaf

\subsection*{Feature analysis}
%Or important features for QT 
Figure~\ref{fig:histograms_supp} displays the number of predicted suitable materials for all approaches (all ML models in an approach agree to a $0.75$ confidence level) as a function of the (a) covalent radius of the elements in the composition, (b) maximum packing efficiency, and standard deviation of the radial distribution function (RDF) with center at (c) $2.0$ and (d) $3.0$. The corresponding figure in the main text shows the standard deviation of the RDF with Gaussian center at $1.0$. Several observations can be made based on the histograms. Panels (e) chemical environment site fingerprint, (f) crystal fingerprint and (g) OP site fingerprint are related to bond orientational parameters, while (h) shows the band gap referenced to the normalized mean of the entire data set.

Firstly, we find that the ...

%histograms 
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.4\textwidth]{figures/histograms/new/ElementProperty_MagpieData range CovalentRadius_count_075.pdf}
    \includegraphics[width=0.4\textwidth]{figures/histograms/new/MaximumPackingEfficiency_max packing efficiency_count_075.pdf}
    \includegraphics[width=0.4\textwidth]{figures/histograms/new/GeneralizedRDF_std_dev Gaussian center=2.0 width=1.0_count_075.pdf}
    \includegraphics[width=0.4\textwidth]{figures/histograms/new/GeneralizedRDF_std_dev Gaussian center=3.0 width=1.0_count_075.pdf}
    \includegraphics[width=0.4\textwidth]{figures/histograms/new/ChemEnvSiteFingerprint_GaussianSymmFuncstd_dev G2_20.0_count_075.pdf}
    \includegraphics[width=0.4\textwidth]{figures/histograms/new/CrystalNNFingerprint_mean tetrahedral CN_4_count_075.pdf} 
    \includegraphics[width=0.4\textwidth]{figures/histograms/new/OPSiteFingerprint_mean tetrahedral CN_4_count_075.pdf} 
    \includegraphics[width=0.4\textwidth]{figures/histograms/new/MP_Eg_count_075.pdf} 
    \caption{Histograms of predicted suitable materials as a function of the (a) covalent radius, (b) maximum packing efficiency, and standard deviation of the radial distribution function with center at (c) $2.0$ and (d) $3.0$. Panels (e) chemical environment site fingerprint, (f) crystal fingerprint and (g) OP site fingerprint are related to bond orientational parameters, while (h) shows the band gap referenced to the normalized mean of the entire data set. The total number of predicted materials is  $6804$ for the Ferrenti approach, $9227$ for the extended Ferrenti approach, and $214$ for the empirical approach. The Ferrenti and extended Ferrenti approaches refer to the left y-axis and the empirical approach to the right. All panels were taken for a $0.75$ cut-off. }
    \label{fig:histograms_supp}
\end{figure}

>>>>

\subsection*{Feature analysis}
%Or important features for QT 
Figure~\ref{fig:histograms_supp} displays the number of predicted suitable materials for all approaches (all ML models in an approach agree to a $0.75$ confidence level) as a function of the (a) covalent radius of the elements in the composition, (b) maximum packing efficiency, and standard deviation of the radial distribution function (RDF) with center at (c) $2.0$ and (d) $3.0$. The corresponding figure in the main text shows the standard deviation of the RDF with Gaussian center at $1.0$. Several observations can be made based on the histograms. Panels (e) chemical environment site fingerprint, (f) crystal fingerprint and (g) OP site fingerprint are related to bond orientational parameters, while (h) shows the material band gaps referenced to the normalized mean of the entire data set.

Firstly, we find that the covalent radii of the materials (see Fig.~\ref{fig:histograms_supp}a) distribute with two peaks in the data in all approaches. The maxima are slightly shifted towards the right for the empirical approach compared to the two others but otherwise the data distributions are similar. The trend of two data peaks is repeated for the maximum packing efficiency (see Fig.~\ref{fig:histograms_supp}b) but is much more prominent for the empirical approach. This indicates that the material density, or in other words the bond length, is an important parameter for QT suitability.

%histograms 
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.4\textwidth]{figures/histograms/new/ElementProperty_MagpieData range CovalentRadius_count_075.pdf}
    \includegraphics[width=0.4\textwidth]{figures/histograms/new/MaximumPackingEfficiency_max packing efficiency_count_075.pdf}
    \includegraphics[width=0.4\textwidth]{figures/histograms/new/GeneralizedRDF_std_dev Gaussian center=2.0 width=1.0_count_075.pdf}
    \includegraphics[width=0.4\textwidth]{figures/histograms/new/GeneralizedRDF_std_dev Gaussian center=3.0 width=1.0_count_075.pdf}
    \includegraphics[width=0.4\textwidth]{figures/histograms/new/ChemEnvSiteFingerprint_GaussianSymmFuncstd_dev G2_20.0_count_075.pdf}
    \includegraphics[width=0.4\textwidth]{figures/histograms/new/CrystalNNFingerprint_mean tetrahedral CN_4_count_075.pdf} 
    \includegraphics[width=0.4\textwidth]{figures/histograms/new/OPSiteFingerprint_mean tetrahedral CN_4_count_075.pdf} 
    \includegraphics[width=0.4\textwidth]{figures/histograms/new/MP_Eg_normalized_databackgrund_075.pdf} 
    \caption{Histograms of predicted suitable materials as a function of the (a) covalent radius, (b) maximum packing efficiency, and standard deviation of the radial distribution function with center at (c) $2.0$ and (d) $3.0$. Panels (e) chemical environment site fingerprint, (f) crystal fingerprint and (g) OP site fingerprint are related to bond orientational parameters, while (h) shows the band gap referenced to the normalized mean of the entire data set. The total number of predicted materials is  $6804$ for the Ferrenti approach, $9227$ for the extended Ferrenti approach, and $214$ for the empirical approach. The Ferrenti and extended Ferrenti approaches refer to the left y-axis and the empirical approach to the right. All panels were taken for a $0.75$ cut-off. }
    \label{fig:histograms_supp}
\end{figure}
